Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-18 doc/report/implementation.tex
added glass photo
resolve conflict

In this section, we detail our implementation on Arduino \cite{Arduino} platform. The whole system is comprised of a glass module, numbers of clients, and a gateway, as shown in the architecture figure (Fig.\,\ref{fig:sysarch}) in last section. We will start from the clients, whose primary tasks are to interface between the Glass and the devices that are attached to it. Then we move on to the implementation of the Glass, who manges users' gesture recognition and communication with clients. The functionality in gateway so far is only minimum to communicate with clients, since it's not the primary focus of this project.

@@

{\color{red} add clients photos here}
\begin{figure}
  \centering
%  \includegraphics[width=\linewidth]{../figs/client.png}
  \caption{Prototype of the clients}
  \label{fig:client}
\end{figure}

The main function of the client is to respond IR signal, and communicate with the Glass to receive corresponding commands. Normally, the client lives in {\it IDLE} mode. When they receive IR signals, indicating the user is expressing interest in interacting with it, the client responds with an XBee acknowledgement and goes into {\it PENDING} state. In this case, since the client doesn't know how many other clients have also responded to the glass, it will wait until a connection signal. If there are multiple clients waiting to be verified by the Glass, the coordination is done at the Glass through sending the right verifying message. To provide visual feedback to the user, the active client that is being verified will blink faster. When it receives the connecting message, it goes to {\it CONNECTED} state and is now ready to take commands. To summarize the clients' behavior, we have a state machine in Fig.\,\ref{fig:clientFSM} for illustration.

@@

Within {\it CONNECTED} state, the clients will react differently according to the device it is connected to. In our prototype, we have two different types of devices. The first is a relay, which can control the whole AC power supply. The interface to relay is simply an digital pin. We only need to set it to {\it LOW} or {\it HIGH}. Such command is transmitted remotely from the Glass through XBee using encoded packet. The second tyep is a computer that is used to play video. To send command to the computer, we have a USB adaptor and a python script taking charge of the translation. We use {\it pyserial} and {\it appscript} in the software. And this enables controlling the play and pause of an video, and system-wide volume control.

@@

The Glass is complicated in two folds. First, we move the complexity of coordinating all clients to the Glass. Second, we have to handle user gesture on Glass. From an engineer perspective, we separate the gesture detection and XBee transmission into two customized library files in Arduino. And only interesting information is exposed to the main program. We use the same Arduino Uno and XBee module as the client. In addition, we have a membrane potentiometer (100 mm long) as the slider to take user's input, and the most important IR emitter to broadcast IR signals. After we've put the components onto the Glass, we have the prototype shown in Fig.\,\ref{fig:glass}.

{\color{red} add glass photos here}
\begin{figure}
  \centering
%  \includegraphics[width=\linewidth]{../figs/glass.png}
  \caption{Prototype of the Glass}
  \label{fig:glass}
\end{figure}

The whole work flow on the Glass is as follows. When the user hasn't shown any interest for interaction, the system stays in {\it IDLE} state. When ``tapping'' is detected, the Glass will broadcast IR signals to inform the devices which are in front of the user. Since we have the tube around the IR transmitter, the resulting signal coverage is a pretty straight line. After the Glass has sent out IR message, at this time, it doesn't know how many devices might respond. In this case, the Glass would wait for a specific period of time, and count the number of acknowledgement messages sent by clients. To ensure responsiveness to end user, we set the timer in {\it WAIT} state to be 1 second. When the timer expires, Glass will go to {\it IDLE} if no client has responded, or {\it CONFIRM} if it receives just one message. However, the complicated case is when there are multiple clients that have received the IR signal (because they are near to each other) and responded. Though we expect this scenario rarely happens, there is still chance when the physical devices are put together and it is necessary to differentiate them. In this case, the system goes to {\it VERIFY} state, and sends out corresponding verifying message based on user's gesture. We adopt the slider on glass to change active selection. Once the user confirmed the selection, it goes to {\it CONNECTED} state and now the Glass is ready to send out commands. We have the FSM in Fig.\,\ref{fig:glassFSM}.

>>>>

In this section, we detail our implementation on Arduino \cite{Arduino} platform. The whole system is comprised of a glass module, numbers of clients, and a gateway, as shown in the architecture figure (Fig.\,\ref{fig:sysarch}) in the last section. We will start from the clients, whose primary tasks are to interface between the Glass and the devices that are attached to it. Then we move on to the implementation of the Glass, which manages user's gesture recognition and communication with the clients. The functionality of the gateway so far is confined to only communicate with the clients, since it's not the primary focus of this project.

@@

{\color{red} add clients photos here}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{../figs/client.jpg}
  \caption{Prototype of the clients}
  \label{fig:client}
\end{figure}

The main function of the client is to respond IR signal and communicate with the Glass to receive commands from the user. Normally, the client stays in {\it IDLE} mode. When it receives an IR signal, suggesting that the user could be interested in interacting with it, the client responds with an XBee acknowledgement and goes into {\it PENDING} state. The glass, after seding the IR, will wait for a certain amoount of time. If there is only one client responding during the wait, the Glass will directly send a connecting message to the only client. When there are multiple clients responding, the Glass will broadcast a verify message with a client ID. The client with a matching ID is called the active client and its LED will blink faster then the others as a visual feedback to the user. After the user decide which one to connect with, the Glass will send out a connecting message. Client turned into {\it CONNECTED} state will be ready to take commands. To summarize the clients' behavior, we have a state machine in Fig.\,\ref{fig:clientFSM} for illustration.

@@

Within {\it CONNECTED} state, the clients will react differently according to the device it is connected to. In our prototype, we have two different types of devices. The first is a relay, which can control the whole AC power supply. The interface to relay is simply an digital pin. We only need to set it to {\it LOW} or {\it HIGH}. Such command is transmitted remotely from the Glass through XBee using encoded packet. The second tyep is a computer that is used to play video. To send command to the computer, we have a USB adaptor and a python script taking charge of the translation. We use the {\it pyserial} and {\it appscript} library to trigger the play, pause command of an video, and system-wide volume control.

@@

The Glass is complicated in two folds. First, we move the complexity of coordinating all clients to the Glass. Second, we have to handle user gesture on Glass. From an engineer perspective, we separate the gesture detection and XBee transmission into two customized library files in Arduino. And only relevant information is sent to the main program. We use the same Arduino Uno and XBee module as the client. An IR emitter is placed within a black tube in order to make the signal a straight beam of light. Then the the tube is attached to the Glass and adjusted in a proper direction. In addition, we have a membrane potentiometer (100 mm long) as the slider to take user's input. After we've put the components onto the Glass, we have the prototype shown in Fig.\,\ref{fig:glass}.

{\color{red} add glass photos here}
\begin{figure}
  \centering
  \includegraphics[width=0.85\linewidth]{../figs/glass.png}
  \caption{Prototype of the Glass}
  \label{fig:glass}
\end{figure}

The whole work flow on the Glass is as follows. When the user hasn't shown any interest for interaction, the Glass stays in {\it IDLE} state. When ``tapping'' is detected, the Glass will send a beam of IR signal to inform the devices which are in front of the user. The Glass waited for a specific period of time and count the number of acknowledgement messages responded by the clients. To ensure responsiveness to end user, we set the timer in {\it WAIT} state to be 1 second. When the timer expires, Glass will go to {\it IDLE} if no client has responded, or {\it CONFIRM} if it receives just one message. However, the complicated case is when there are multiple clients that have received the IR signal (because they are near to each other) and responded. Though we expect this scenario rarely happens, there is still chance when the physical devices are put together and it is necessary to differentiate them. In this case, the system goes to {\it VERIFY} state, and sends out corresponding verifying message based on user's gesture. The user can slide back and forth to select the desired target. Once the user confirmed the selection and release his finger, it goes to {\it CONNECTED} state and now the Glass is ready to send out commands. We have the FSM in Fig.\,\ref{fig:glassFSM}.
